\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

@@

Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{evans_1994} \citep[see also][]{dawe_2008}.

The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.

>>>>

%%%%%%%%%%%% 
\subsection{Initial Model Validation}\label{section:results_validation}

@@

Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.

\medskip
Another numerical simulation was performed in slightly modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10. Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994} (\red{ .... COMMENT THE RESULTS OBTAINED AND COMPARE IT WITH EVANS WORK ...})

\red{KOSTAS ... HAVE A LOOK IN FIG.~\ref{fem_cv_represent_abc} ... SATURATION PROFILES DO NOT SEEM TO MATCH ...}

\medskip
In this section three \red{(??)} different sets of simulations were explained. Starting from an initial square set-up to validate the existance of cross flow and how the simulator works, we moved to a larger domain by increasing the aspect ratio. The reason was to give more time, space and greater number of elements to our simulator and again see how the front/cross-flow will develop. The third test-case is based in the initial and boundary condition of the second set of simulations. Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:6a}-%\ref{fig:6b},
\ref{fig:6c}) and how the cross-flow as well as the simulation will progress on time. The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.

\medskip
\noindent
\red{QUICK QUESTIONS ... \\
\noindent
A) FOR THE FIRST TEST-CASE, WAS THE SIMULATION PERFORMED IN A SQUARED DOMAIN (FROM THE PICS, IT SEEMS TO BE RECTANGULAR)? \\ B) THUS ASSUMING THAT THE FIRST DOMAIN WAS RECTANGULAR, THUS IT IS THE SAME AS THE SECOND SIMULATION! THUS WHY THE SATURATION PROFILE IS DIFF (FOR VR=1) FROM SIMULATION 1??? \\
\noindent
C) ALSO: DO NOT USE 'WE' IN TECHNICAL TEXT ... IT DOES REALLY DOWNGRADE IT !!! }

%%%%%%%%%%%%  
\subsection{Flow Simulations in Hele-Shaw Cells at Several Viscosity Ratio Conditions}\label{section:results_homo_hete}

In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following \citet{saffman_1986} work. In this work, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem formulation and solution.

Here, 2D simulations are conducted in 5$\times$5 domain, Fig.~\ref{fig:homoheleshaw}(a) fully saturated with a fluid. Wetting phase fluid is injected from the bottom left-hand corner of the domain with velocity of $\frac{\sqrt{2}}{2}$. A zero-flux condition was applied to all boundaries, except the top right-hand corner (named as sink).
XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
 of the problem. formation and stability of viscous flow instaseminal work of \citet{saffman_1986}
Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in figures \ref{fig:1a_homoheleshaw_3}-%,\ref{fig:1b_homoheleshaw_3} 
\ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations. In all cases, simulations were performed in a squared geometry of $5\times5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
. The sink (pressure set to $0$) is allocated in the top right hand side corner of the domain. Newmann boundary conditions %(i.e., no flux) 
was imposed to all borders of the domain except at the top righ hand side corner. The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter, homogeneous and heterogeneous domain is used.

### 2017-06-19 Papers/ViscousInstabilities/article_figure1.tex
Start updating Results Section 4.2

@@

>>>>

%%%
%%% FIGURE
%%%
\begin{landscape}
  \begin{figure}[ht]
    \vbox{ 
      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} }
      \vspace{0.cm}
      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}}}
\caption{\red{THIS IS JUST FOR OUR OWN COMPARISON ... IT DOESN'T SEEM TO MATCH ... }}
\label{fem_cv_represent_abc}
\end{figure}
\end{landscape}
\clearpage
%%%
%%%
%%%

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}
\vspace{0.cm}
\hbox{\hspace{1.0cm} (a) Hell-Shaw cell domain \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=1000\red{(???)}}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}}
\vspace{0.cm}
\hbox{ \hspace{2.cm} (d) t=2500\red{(???)} \hspace{3.0cm} (e) t=1000\red{(???)}   \hspace{4.cm} (f) t=XXX\red{(???)}}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell: (a) source and sink regions are explicitly shown along with prescribed dimensions; (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves. The domain contains \red{XX} \PN[1]{2} elements and {\it VR}=1.}
\label{fig:homoheleshaw}
\end{figure}
\end{landscape}
\clearpage
